\plaintitle

### 2017-06-05 papers/IoT2017/paper.tex
no message

\usepackage{paralist}

@@

@@

\section{Analysis}
\label{sec:analysis}

@@

@@

>>>>

\usepackage{paralist}
\usepackage{enumitem}

@@

\allowdisplaybreaks

@@

\section{Discussion}
\label{sec:discussion}

@@

Most of our security requirements follow readily from 
\begin{compactitem}
\item the non-malleability of transactions in the distributed ledger 
\item the signature based validation of transactions
\item tamper-resistance of smart meters.
\end{compactitem}

@@

First, we can easily see that the net amount of energy sold by a prosumer for each timestep is at most $\field{MAXEPA}_i$.
The amount of energy sold by the prosumer for a timetep is less than or equal to the amount of EPA obtained for that timestep.
The prosumer can withdraw $\field{MAXEPA}_i$ amount of EPA from its smart meter.
However, to obtain any amount of further EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
Similarly, the net amount of energy sold is at most $\field{MAXECA}_i$.

Second, we can see that the amount of bids posted at the same time by prosumer $i$ for timestep $t$ is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.

### 2017-06-05 papers/IoT2017/services.tex
no message

Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.

\subsubsection{Communication Anonymity}
Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

@@

\subsubsection{Bidding Anonymity}
Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
\begin{itemize}
\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
\end{itemize}

>>>>

In this subsection, we describe the services on which transactions are built and which build on transactions.
We have already discussed distributed ledgers, which permanently store transactions.
Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\todo{Revise list based on final organization!}

\subsubsection{Communication Anonymity}
Firstly, we must provide an anonymous communication layer, on which we can build all other services within our system.
Without this communication layer, transactions and bids could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
In practice, this service can built on 
%In our first implementation, we can use
 the free and open-source Tor software with private Directory Authorities.
In this case, anonymous communication addresses in bids and asks correspond to public-keys that identify Tor hidden services.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

@@

\subsubsection{Bidding Anonymity}
Finally, we must provide prosumers with the ability to post energy bids and asks anonymously.
To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
\begin{itemize}
\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
\end{itemize}

\subsubsection{Billing and Microgrid Control}

The energy consumption balance $E_i^t$ of prosumer $i$ in timeslot~$t$ is
\begin{align*}
E_i^t = & \hphantom{+} \text{measured consumption} - \text{measured production} \\
 & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
\end{align*}
Notice that energy consumption assets are not necessary for billing, they are only used to enforce safety requirements.

The financial balance $F_i^t$ of prosumer $i$ in timeslot $t$, which is to be paid by the prosumer to the DSO, is
\begin{align*}
F_i^t = & \hphantom{+} \text{FA deposited by $i$ in $t$} - \text{FA withdrawn by $i$ in $t$} \\
 & + \begin{cases}
E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
- E_i^t \cdot \field{priceConsumption} & \text{ otherwise.} 
\end{cases}
\end{align*}

\TODO{discussion of microgrid control based on bids and trades? (update subsubsection title)}

### 2017-06-05 papers/IoT2017/solution.tex
no message

\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(onion routing)};

\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(blockchain)};

>>>>

\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(e.g., onion routing)};

\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(e.g., blockchain)};

### 2017-06-05 papers/IoT2017/transactions.tex
no message

The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
Since these transactions provide a diverse set of functionality, they are divided into two types.

\TODO{For brevity, combine regulatory transactions into one type.}

The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
These transactions contain the following fields:
\begin{compactitem}
\item \field{allow}: list of smart meters to be authorized, each of which is defined by
\begin{compactitem}
\item \field{id}: identifier of the smart meter.
\item \field{pubkey}: public key of the smart meter,
\end{compactitem}
\item \field{ban}: list of identifiers of smart meters to be banned, 
\item \field{timestep}: timestep in which authorizations and bans should take effect,
\item \field{sig}: DSO's signature over the transaction.
\end{compactitem}

A regulatory transaction of this type is valid if %the following two conditions hold:
%\begin{compactitem}
%\item 
\field{timestep} is not in the past and % specified in the transaction is in the future.
%\item 
the DSO's signature is valid.
%\end{compactitem}

>>>>

The DSO uses regulatory transactions for two purposes: to manage authorized smart meters and to set a price policy.
First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
Whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be malfunctioning or compromised), the DSO notifies the microgrid by banning the device.
Second, to influence microgrid load, the DSO can set a price policy, which includes a price at which prosumer may buy energy from the DSO and a price at which they may sell energy to the DSO.

A regulatory transactions contain the following fields:
\begin{compactitem}
\item \field{authorize}: list of smart meters to be authorized, each of which is defined by
\begin{compactitem}
\item \field{id}: identifier of the smart meter,
\item \field{pubkey}: public key of the smart meter,
\end{compactitem}
\item \field{ban}: list of identifiers of smart meters to be banned, 
\item \field{priceConsumption}: price at which DSO sells energy,
\item \field{priceProduction}: price at which DSO buys energy,
\item \field{time}: timestep after which authorizations, bans, and price changes should take effect,
\item \field{sig}: DSO's signature over the transaction.
\end{compactitem}

A regulatory transaction of this type is valid if %the following two conditions hold:
%\begin{compactitem}
%\item 
\field{timestep} is not in the past and % specified in the transaction is in the future.
%\item 
the DSO's signature is valid.
%\end{compactitem}
%
The active prices for timestep $t$ are given by the last regulatory transaction recorded on the ledger whose \field{time} is less than $t$.
Similarly, later regulatory transactions recorded on the ledger override the authorization and bans of earlier transactions.
